A Global Genome-wide Scan with Optimal Cutoff Mining for Emerging Biomarkers in Head and Neck Squamous Cell Carcinoma

### 2021-03-16 main.tex
Updates from Overleaf

*** make Figure 5 holistic:
%meridian and emotion has mutual reaction
%meridian effect tissue and organ
%(autonomic nerve system, myofascial network, prefrontal cortex)
%placebo-effect influence on drug discovery
%gene expression in deep learning
%Ching, T. et al. Opportunities and obstacles for deep learning in biology and medicine. J. R. Soc. Interface 15, (2018).
%慈悲心 利他心
%博士班學生，越研究越發現，科學的不足，心理與靈性的力量，更是背後推動的冥冥力量，身心靈是合一的
%#正念 除了可以減壓，還可以治癒疼痛
%Environment 改造患者的心，就能改造他的身體環境，有利消除癌症

>>>>

%*** make Figure 5 holistic: Figure_5_holisticCare.pdf
\begin{figure}[hp]
\centering
\includegraphics[width=14cm]{Figure_5_holisticCare.pdf}
\bcaption{The concept of holistic care for \acrshort{hnscc} patients.}
{Beyond carcinogenesis - Under the mind-brain-body axis, a stressful environment will trigger emotional reception. The subconscious mind (brain) will release stress hormones and inflammation signals in response to the emotion. The physical body's internal environment (cells) alters epigenetic control in gene regulation and mRNA expression. In a long incubation time, the tissue/cells will be transformed into dysplasia then malignancy with helping from known carcinogens.\\
Cancer care - Holistic care should take care of cancer patients' spiritual, emotional, physical, and socioeconomic needs. Physical care will be carried out by medication therapy or surgery. After establishing a therapeutic relationship, the physicians' spiritual properties (empathy, sympathy, and compassion) will engage their patients and recover their self-compassion to gain resilience against the disease.\\
Suggested health care record - Besides physical, pathological, or psychological data, electric healthcare records (EHR) and \acrshort{tcga} should collect "holistic features".}
\label{fig:figure5}
\end{figure}
%meridian and emotion has mutual reaction
%meridian effect tissue and organ
%(autonomic nerve system, myofascial network, prefrontal cortex)
%placebo-effect influence on drug discovery
%gene expression in deep learning
%Ching, T. et al. Opportunities and obstacles for deep learning in biology and medicine. J. R. Soc. Interface 15, (2018).
%慈悲心 利他心
%博士班學生，越研究越發現，科學的不足，心理與靈性的力量，更是背後推動的冥冥力量，身心靈是合一的
%#正念 除了可以減壓，還可以治癒疼痛
% modify the dark environment 改造患者的心，就能改造他的身體環境，有利消除癌症
